On The Subspace Learning for Network Attack Detection

### 2019-06-16 docs/thesis/parts/3_m_rpca.tex
new template

\begin{quotation}[]{Paulo Freire}
No one knows it all. No one is ignorant of everything. We all know something. We are all ignorant of something.
\end{quotation}

@@

\begin{figure}[!htb]
	\centering
	\subfigure[Pareto and Gaussian Anomalies]{%
		\includegraphics[width=0.48\textwidth]{figures/ch4/4_Xpg2.png}
		\label{fig:4.01}
	}
	\subfigure[Lognormal and Gaussian Anomalies]{%
		\includegraphics[width=0.48\textwidth]{figures/ch4/4_Xlogng2.png}
		\label{fig:4.02}
	}
	\caption[Examples of skewed and heavy tailed distributions]{Examples of skewed and heavy tailed distributions}
	\label{fig:4.03}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/ch4/4_Xgu2.png}
	\caption{Example of Gaussian and Uniform Anomalies}
	\label{fig:4.04}
\end{figure}

@@

\begin{figure}[!htb]
	\centering
	\subfigure[State of scenario 16.]{%
		\includegraphics[width=0.47\textwidth]{figures/ch4/raw_distplot_capture20110816_State.png}
		\label{fig:4.05}
	}
	\subfigure[Destination Type of service of scenario 10.]{%
		\includegraphics[width=0.47\textwidth]{figures/ch4/raw_distplot_capture20110810_dTos.png}
		\label{fig:4.06}
	}
	\caption[Skewness and Overlapping]{Example of skewness and overlapping}
	\label{fig:4.07}
\end{figure}

@@

\begin{figure}[!htb]
	\centering
	\subfigure[State of scenario 10.]{%
		\includegraphics[width=0.47\textwidth]{figures/ch4/raw_distplot_capture20110810_State.png}
		\label{fig:4.08}
	}
	\subfigure[Source Port of scenario 16.]{%
		\includegraphics[width=0.47\textwidth]{figures/ch4/raw_distplot_capture20110816_Sport.png}
		\label{fig:4.09}
	}
	\caption[Skewness and Overlapping]{Skewness and Overlapping}
	\label{fig:4.10}
\end{figure}

@@

\begin{algorithm}
	\label{alg:4.01}
	\SetAlgoLined
	\KwResult{$\bar{\pmb{t}}_{\bar{\pmb{x}}}$, $\bar{\pmb{t}}_{\bar{\pmb{s}}}$, $\bar{\pmb{t}}_{\bar{\pmb{k}}}$}
	Given $\pmb{X}$ split into $\pmb{X}^s$ and $\pmb{X}^c$\;
	\While{not $\min_{L,S}\left \| \pmb{L} \right \|_{*} + \lambda \left \| \pmb{S} \right \|_{1}$ of $\pmb{X}^s$}{
		$\pmb{L}_{k+1} \in \operatorname*{argmin}_{\pmb{L} \in \mathbb{R}^{m \times n}}\{l(\pmb{L}, \pmb{S}_{k}, \pmb{Y}_{k})\}$\;
		$\pmb{S}_{k+1} \in \operatorname*{argmin}_{\pmb{S} \in \mathbb{R}^{m \times n}}\{l(\pmb{L}_{k+1}, \pmb{S}, \pmb{Y}_{k})\}$\;
		$\pmb{Y}_{k+1} = \pmb{Y}_{k} + \mu(\pmb{X} - \pmb{L}_{k} - \pmb{S}_{k})$\;
	}
	$\bar{\pmb{x}} = \displaystyle\frac{1}{h}\displaystyle\sum_{i\in \pmb{h}} \pmb{x}_i$, for $\pmb{L}^s$\;
	$\bar{\pmb{\Sigma}} = \displaystyle\frac{1}{h}\displaystyle\sum_{i\in \pmb{h}} (\pmb{x}_i - \bar{\pmb{x}})(\pmb{x}_i - \bar{\pmb{x}})^\prime$, for $\pmb{L}^s$\;
	$\bar{\pmb{s}} = \frac{\pmb{m}_3}{\pmb{m}_2^{\frac{3}{2}}}$, for $\pmb{L}^s$\;
	$\bar{\pmb{k}} = \frac{\pmb{m}_4}{\pmb{m}_2^2}$, for $\pmb{L}^s$\;
	$\pmb{d}(\pmb{x},\bar{\pmb{x}}, \bar{\pmb{\Sigma}}) = \sqrt{(\pmb{x} - \bar{\pmb{x}}) \bar{\pmb{\Sigma}}^{-1}(\pmb{x} - \bar{\pmb{x}})^\prime}$\;
	$\pmb{d}(\pmb{x}, \bar{\pmb{s}}, \bar{\pmb{\Sigma}}) = \sqrt{(\pmb{x} - \bar{\pmb{s}}) \bar{\pmb{\Sigma}}^{-1}(\pmb{x} - \bar{\pmb{s}})^\prime}$\;
	$\pmb{d}(\pmb{x}, \bar{\pmb{k}}, \bar{\pmb{\Sigma}}) = \sqrt{(\pmb{x} - \bar{\pmb{k}}) \bar{\pmb{\Sigma}}^{-1}(\pmb{x} - \bar{\pmb{k}})^\prime}$\;
	$\bar{\pmb{t}}_{\bar{\pmb{x}}} = [\pmb{d}(\pmb{x}, \bar{\pmb{x}}, \bar{\pmb{\Sigma}})]^c$\;
	$\bar{\pmb{t}}_{\bar{\pmb{s}}} = [\pmb{d}(\pmb{x}, \bar{\pmb{s}}, \bar{\pmb{\Sigma}})]^c$\;
	$\bar{\pmb{t}}_{\bar{\pmb{k}}} = [\pmb{d}(\pmb{x}, \bar{\pmb{k}}, \bar{\pmb{\Sigma}})]^c$\;
	\caption{Moment Distances from Robust Subspace}
\end{algorithm}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=10cm]{figures/ch4/gaussian_f1_contamination.png}
	\caption{Anomaly detection on Gaussian distributed with uniform anomalies}
	\label{fig:4.10}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=10cm]{figures/ch4/pareto_f1_contamination.png}
	\caption{Anomaly detection on Pareto distributed with Gaussian anomalies}
	\label{fig:4.11}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=10cm]{figures/ch4/lognormal_f1_contamination.png}
	\caption{Anomaly detection on Lognormal distributed with Gaussian anomalies}
	\label{fig:4.12}
\end{figure}

>>>>

@@

\begin{figure}[!htb]
	% \centering
	% \subfigure[Pareto and Gaussian Anomalies]{%
	% 	\includegraphics[width=0.48\textwidth]{figs/ch4/4_Xpg2.png}
	% 	\label{fig:4.01}
	% }
	% \subfigure[Lognormal and Gaussian Anomalies]{%
	% 	\includegraphics[width=0.48\textwidth]{figs/ch4/4_Xlogng2.png}
	% 	\label{fig:4.02}
	% }
	% \caption[Examples of skewed and heavy tailed distributions]{Examples of skewed and heavy tailed distributions}
	% \label{fig:4.03}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figs/ch4/4_Xgu2.png}
	\caption{Example of Gaussian and Uniform Anomalies}
	\label{fig:4.04}
\end{figure}

@@

\begin{figure}[!htb]
	% \centering
	% \subfigure[State of scenario 16.]{%
	% 	\includegraphics[width=0.47\textwidth]{figs/ch4/raw_distplot_capture20110816_State.png}
	% 	\label{fig:4.05}
	% }
	% \subfigure[Destination Type of service of scenario 10.]{%
	% 	\includegraphics[width=0.47\textwidth]{figs/ch4/raw_distplot_capture20110810_dTos.png}
	% 	\label{fig:4.06}
	% }
	% \caption[Skewness and Overlapping]{Example of skewness and overlapping}
	% \label{fig:4.07}
\end{figure}

@@

\begin{figure}[!htb]
	% \centering
	% \subfigure[State of scenario 10.]{%
	% 	\includegraphics[width=0.47\textwidth]{figs/ch4/raw_distplot_capture20110810_State.png}
	% 	\label{fig:4.08}
	% }
	% \subfigure[Source Port of scenario 16.]{%
	% 	\includegraphics[width=0.47\textwidth]{figs/ch4/raw_distplot_capture20110816_Sport.png}
	% 	\label{fig:4.09}
	% }
	% \caption[Skewness and Overlapping]{Skewness and Overlapping}
	% \label{fig:4.10}
\end{figure}

@@

\begin{algorithm}
	\label{alg:4.01}
	% \SetAlgoLined
	% \KwResult{$\bar{\pmb{t}}_{\bar{\pmb{x}}}$, $\bar{\pmb{t}}_{\bar{\pmb{s}}}$, $\bar{\pmb{t}}_{\bar{\pmb{k}}}$}
	% Given $\pmb{X}$ split into $\pmb{X}^s$ and $\pmb{X}^c$\;
	% \While{not $\min_{L,S}\left \| \pmb{L} \right \|_{*} + \lambda \left \| \pmb{S} \right \|_{1}$ of $\pmb{X}^s$}{
	% 	$\pmb{L}_{k+1} \in \operatorname*{argmin}_{\pmb{L} \in \mathbb{R}^{m \times n}}\{l(\pmb{L}, \pmb{S}_{k}, \pmb{Y}_{k})\}$\;
	% 	$\pmb{S}_{k+1} \in \operatorname*{argmin}_{\pmb{S} \in \mathbb{R}^{m \times n}}\{l(\pmb{L}_{k+1}, \pmb{S}, \pmb{Y}_{k})\}$\;
	% 	$\pmb{Y}_{k+1} = \pmb{Y}_{k} + \mu(\pmb{X} - \pmb{L}_{k} - \pmb{S}_{k})$\;
	% }
	% $\bar{\pmb{x}} = \displaystyle\frac{1}{h}\displaystyle\sum_{i\in \pmb{h}} \pmb{x}_i$, for $\pmb{L}^s$\;
	% $\bar{\pmb{\Sigma}} = \displaystyle\frac{1}{h}\displaystyle\sum_{i\in \pmb{h}} (\pmb{x}_i - \bar{\pmb{x}})(\pmb{x}_i - \bar{\pmb{x}})^\prime$, for $\pmb{L}^s$\;
	% $\bar{\pmb{s}} = \frac{\pmb{m}_3}{\pmb{m}_2^{\frac{3}{2}}}$, for $\pmb{L}^s$\;
	% $\bar{\pmb{k}} = \frac{\pmb{m}_4}{\pmb{m}_2^2}$, for $\pmb{L}^s$\;
	% $\pmb{d}(\pmb{x},\bar{\pmb{x}}, \bar{\pmb{\Sigma}}) = \sqrt{(\pmb{x} - \bar{\pmb{x}}) \bar{\pmb{\Sigma}}^{-1}(\pmb{x} - \bar{\pmb{x}})^\prime}$\;
	% $\pmb{d}(\pmb{x}, \bar{\pmb{s}}, \bar{\pmb{\Sigma}}) = \sqrt{(\pmb{x} - \bar{\pmb{s}}) \bar{\pmb{\Sigma}}^{-1}(\pmb{x} - \bar{\pmb{s}})^\prime}$\;
	% $\pmb{d}(\pmb{x}, \bar{\pmb{k}}, \bar{\pmb{\Sigma}}) = \sqrt{(\pmb{x} - \bar{\pmb{k}}) \bar{\pmb{\Sigma}}^{-1}(\pmb{x} - \bar{\pmb{k}})^\prime}$\;
	% $\bar{\pmb{t}}_{\bar{\pmb{x}}} = [\pmb{d}(\pmb{x}, \bar{\pmb{x}}, \bar{\pmb{\Sigma}})]^c$\;
	% $\bar{\pmb{t}}_{\bar{\pmb{s}}} = [\pmb{d}(\pmb{x}, \bar{\pmb{s}}, \bar{\pmb{\Sigma}})]^c$\;
	% $\bar{\pmb{t}}_{\bar{\pmb{k}}} = [\pmb{d}(\pmb{x}, \bar{\pmb{k}}, \bar{\pmb{\Sigma}})]^c$\;
	\caption{Moment Distances from Robust Subspace}
\end{algorithm}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=10cm]{figs/ch4/gaussian_f1_contamination.png}
	\caption{Anomaly detection on Gaussian distributed with uniform anomalies}
	\label{fig:4.10}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=10cm]{figs/ch4/pareto_f1_contamination.png}
	\caption{Anomaly detection on Pareto distributed with Gaussian anomalies}
	\label{fig:4.11}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=10cm]{figs/ch4/lognormal_f1_contamination.png}
	\caption{Anomaly detection on Lognormal distributed with Gaussian anomalies}
	\label{fig:4.12}
\end{figure}

### 2019-06-16 docs/thesis/parts/4_mobile.tex
new template

\begin{quotation}[]{Confucius}
Life is really simple, but we insist on making it complicated.
\end{quotation}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figures/ch3/fig01.eps}
	\caption{The core set of functions and protocols of the mobile cloud security infrastructure}
	\label{fig:3_01}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=12cm]{figures/ch3/fig02.eps}
	\caption{The Client-side Architecture}
	\label{fig:3_02}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=15cm]{figures/ch3/fig03.eps}
	\caption{Proposed Architecture for Offline Mobile Security}
	\label{fig:3_03}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=10cm]{figures/ch3/fig06.eps}
	\caption{The Threat Intelligence Manager Workflow}
	\label{fig:3_06}
\end{figure}

>>>>

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{figs/ch3/fig01.eps}
	\caption{The core set of functions and protocols of the mobile cloud security infrastructure}
	\label{fig:3_01}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=12cm]{figs/ch3/fig02.eps}
	\caption{The Client-side Architecture}
	\label{fig:3_02}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=15cm]{figs/ch3/fig03.eps}
	\caption{Proposed Architecture for Offline Mobile Security}
	\label{fig:3_03}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=10cm]{figs/ch3/fig06.eps}
	\caption{The Threat Intelligence Manager Workflow}
	\label{fig:3_06}
\end{figure}

### 2019-06-16 docs/thesis/parts/b_csf_pca_svm.tex
new template

\begin{figure}[h!]
     \centering 
     \includegraphics[height=10cm, width=10cm]{figures/ch2/raw_igovti_covariance.eps}
     \caption{Covariance matrix of iGovTI questions.}
     \label{fig:ch2_fig1}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=8cm, width=11cm]{figures/ch2/raw_variance_ecdf.eps}
     \caption{Empirical CDF of variance.}
     \label{fig:ch2_fig2}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=8cm, width=11cm]{figures/ch2/raw_igovti_ranking_pc2.eps}
     \caption{iGovTI ranking from 2 principal components.}
     \label{fig:ch2_fig3}
\end{figure}

>>>>

\begin{figure}[h!]
     \centering 
     \includegraphics[height=10cm, width=10cm]{figs/b_csf_pca_svm/raw_igovti_covariance.eps}
     \caption{Covariance matrix of iGovTI questions.}
     \label{fig:ch2_fig1}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=8cm, width=11cm]{figs/b_csf_pca_svm/raw_variance_ecdf.eps}
     \caption{Empirical CDF of variance.}
     \label{fig:ch2_fig2}
\end{figure}

@@

\begin{figure}[h!]
     \centering 
     \includegraphics[height=8cm, width=11cm]{figs/b_csf_pca_svm/raw_igovti_ranking_pc2.eps}
     \caption{iGovTI ranking from 2 principal components.}
     \label{fig:ch2_fig3}
\end{figure}

### 2019-06-16 docs/thesis/thesis.tex
new template

% class
\documentclass[en, oneside, onehalfspacing]{risethesis}

% packages and configurations
\usepackage{enumitem}
\usepackage{lineno, hyperref}
\usepackage[numbers]{natbib}
\usepackage{babel}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{color, colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{amsthm,amsmath}
\usepackage{mathtools}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{courier}
\usepackage{amsfonts}
\usepackage{morefloats}
\usepackage{lipsum}
\usepackage{cleveref}
\usepackage{hyperref}

\newtheorem{thm}{Scenario}
\hypersetup{breaklinks=true}
\urlstyle{same}
\Urlmuskip=0mu plus 1mu\relax
\lstset{numbers=left, 
	stepnumber=1, 
	firstnumber=1, 
	numberstyle=\tiny, 
	extendedchars=true, 
	breaklines=true,
	frame=tb,
	basicstyle=\footnotesize, 
	stringstyle=\ttfamily,
	showstringspaces=false
}

\definecolor{lightgray}{gray}{0.8}
\definecolor{Gray}{gray}{0.9}
\renewcommand{\lstlistingname}{Code}
\renewcommand{\lstlistlistingname}{Lista de Listagens}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand*\justify{%
	\fontdimen2\font=0.4em% interword space
	\fontdimen3\font=0.2em% interword stretch
	\fontdimen4\font=0.1em% interword shrink
	\fontdimen7\font=0.1em% extra space
	%\hyphenchar\font=`\-% allowing hyphenation
}

\address{BRASÍLIA}

\universitypt{Universidade de Brasília}
\universityen{Universidade de Brasília}

\departmentpt{Departamento de Engenharia Elétrica - ENE/FT}
\departmenten{Departamento de Engenharia Elétrica - ENE/FT}

\programpt{Progama de Pós-Graduação em Engenharia Elétrica - PPGEE}
\programen{Progama de Pós-Graduação em Engenharia Elétrica - PPGEE}

\majorfieldpt{Engenharia Elétrica}
\majorfielden{Electrical Engineering}

\title{Discriminative Sensing Based on Signal Processing for Information Security Analysis}
\date{November/2017}

\author{Thiago Pereira de Brito Vieira}
\adviser{João Paulo Carvalho Lustosa da Costa}
% \coadviser{?}

\begin{document}

\frontmatter
\frontpage
\presentationpage

\begin{dedicatory}Ficha Catalográfica\end{dedicatory}

\begin{dedicatory}Signatures\end{dedicatory}

\begin{dedicatory}Dedicatory.\end{dedicatory}

\agradecimentos
First and foremost, I would like to thank God for giving me the life, strength, knowledge and opportunity to undertake this research study and to ..

(...)

Thank You!!

\begin{epigraph}[]{Confucius}
	Wherever you go, go with all your heart.
\end{epigraph}

\resumo
\input{chapters/resumo}

\abstract
\input{chapters/abstract}

\tableofcontents

\makeatletter
\renewcommand{\@thesubfigure}{\thesubfigure:\hskip\subfiglabelskip}
\makeatother
\setcounter{lofdepth}{2}

\listoffigures
\listoftables

\input{chapters/acronyms}
\mainmatter

\include{chapters/1_introduction/introduction}
\include{chapters/2_eigen_similarity/eigen_similarity}
\include{chapters/3_mobile/mobile}
\include{chapters/4_tensor_dl/tensor_dl}
\include{chapters/5_conclusion_future_work/conclusion}

\appendix
\include{chapters/appendix/a_mos/a_mos}
\include{chapters/appendix/b_pca_svm_cfa/pca_svm_cfa}

\bibliographystyle{natbib}
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{references}

\clearpage
\addappheadtotoc

>>>>

%% These files were modified in Lyx by:
%           Lus F. C. Fgueiredo, Fev., 2017.
%% Git repo for Lyx version are available at:
%%          https://github.com/lara-unb/DOCUMENTS/tree/master/templates
%% Latex version for sharelatex and overleaf v2 ported by:
%%          Vinícius Galvão Guimarães
%% 
%% Contributions of:
%%          Miguel Eduardo Gutierrez Paredes
%% LyX 2.2.3 created this file.  For more info, see http://www.lyx.org/.

%\documentclass[11pt,oneside,portuguese]{book}
\documentclass[12pt,oneside,english]{book}
\input{setup/packages}
\input{setup/other}
\input{setup/theorem_lemma}
\input{setup/languages}
\input{setup/listing_def}
\input{setup/glossaries_setup}

\makeatother
\begin{document}
\pagenumbering{roman}

\input{setup/title_author_etc}
\input{parts/dedicated_to}

\runfrontend{}

\import{}{macros}
\import{parts/}{abstract}

\sumario

\listadefiguras

% \listadetabelas

%-----------------------------------------------
% Use os simbolos, acronimos e notacoes com as funcoes a seguir
% To use this acronyms list, check the file glossaries-list/symbos.tex.
	\listadesimbolos

% To use this acronyms list, check the file glossaries-list/acronyms.tex.
	\listadeacronimos

% To use this acronyms list, check the file glossaries-list/notation.tex.
	\listadenotacoes
%-----------------------------------------------

\markboth{}{}

%Main Body
\mainmatter 
\setcounter{page}{1} \pagestyle{plain}

\import{parts/}{1_introduction}
\import{parts/}{2_eigen_similarity}
\import{parts/}{3_m_rpca}
\import{parts/}{4_mobile}
\import{parts/}{5_conclusion}

%BIBLIOGRAPHY
\addcontentsline{toc}{chapter}{REFERENCES}
% Do not use \bibliographystyle{IEEEtran} with abntex2cite package!!!!!
% Also, try not to use abntex2cite at all! just comment its package in setup/packages.tex
%\bibliographystyle{chicago}
%\bibliographystyle{acm}
\bibliographystyle{IEEEtran}

\bibliography{bibliography}

%APPENDIX
\part*{APPENDIX}
\appendix
\import{parts/}{a_mos}
\import{parts/}{b_csf_pca_svm}
